---
title: "Inaction We Trust"
author: "Adrien Fillon"
date: "27/01/2021"
output:
  word_document:
    toc: yes
    toc_depth: '3'
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

list.of.packages <- c("report", "dplyr", "psych", "ggplot2", "tidyverse", "corrr", "corrplot", "PerformanceAnalytics", "Hmisc", "ggstatsplot", "jtools", "metan", "ggstatsplot", "ggthemes", "ggpubr", "apaTables","insight", "parameters")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[
  ,"Package"])]
if(length(new.packages)) install.packages(new.packages, dependencies = TRUE)
invisible(lapply(list.of.packages, library, character.only = TRUE))

# setting formatting options
options(scipen=999, digits =3)

```

# Study 1a

```{r study1, echo=FALSE}

data1 <- read.csv("inactionwetrust_study1.csv", na.strings=c("","NA"))

# data cleaning
## remove variable descriptions + practice data
data1 <- data1[-c(1:1),]
data1 <-  data1 [, c("preference", "competence", "norms", "Q55", "check1",
                     "check2", "check3", "sex", "Age")] 
# rename and summarize descriptives
data1$preference <- as.numeric(data1$preference)
data1$competence <- as.numeric(data1$competence)
data1$normative <- as.numeric(data1$norms)
data1<-rename(data1, regret = Q55)
data1$regret <- as.numeric(data1$regret)
data1$age<- as.numeric(data1$Age)

summary1 <- data1 %>%
    select(preference, competence, normative, regret, sex, age) %>% 
  psych::describe(quant=c(.25,.75)) %>% as_tibble(rownames="rowname")
knitr::kable(summary1, digits=2, caption = "Summary study 1a", align = "c")
tablegender1<-table(data1$sex)
knitr::kable(tablegender1, digits=2, caption = "Summary gender", align = "c")


dplot1 <- data1 %>% select(preference, competence, normative, regret)%>%
  rename(Preference = preference, Competence = competence, Norms = normative, Regret = regret)%>%
  gather()
dplot1$key<-factor(dplot1$key, levels = c("Preference","Competence", "Norms", "Regret"))

dplot1  %>% ggplot(aes(value)) +
  facet_wrap(~ key, scales = "free", )+ geom_histogram(binwidth = 1)+theme_apa()+
  labs(x = "", y = "")+ scale_x_continuous(limits = c(-5, 5))+ ylim(0, 200)

Sa1preferenceplot <- ggstatsplot::gghistostats(
  data = data1, # data from which variable is to be taken
  x = preference, # numeric variable
  xlab = "Preference", # x-axis label
  # title = "Preference", # title for the plot
  #ggtheme = ggthemes::theme_tufte(), # changing default theme
  test.value = 0, # test value
  #caption = "Data courtesy of: SAPA project (https://sapa-project.org)"
)
Sa1preferenceplot
ggsave("Study1a-preference.png", dpi = 600, scale = 1.7)

Sa1competenceplot <- ggstatsplot::gghistostats(
  data = data1, # data from which variable is to be taken
  x = competence, # numeric variable
  xlab = "Competence", # x-axis label
  # title = "Competence", # title for the plot
  #ggtheme = ggthemes::theme_tufte(), # changing default theme
  test.value = 0, # test value
  #caption = "Data courtesy of: SAPA project (https://sapa-project.org)"
)
Sa1competenceplot
ggsave("Study1a-competence.png", dpi = 600, scale = 1.7)


Sa1normativeplot <- ggstatsplot::gghistostats(
  data = data1, # data from which variable is to be taken
  x = normative, # numeric variable
  xlab = "Norms", # x-axis label
  # title = "Norms", # title for the plot
  #ggtheme = ggthemes::theme_tufte(), # changing default theme
  test.value = 0, # test value
  #caption = "Data courtesy of: SAPA project (https://sapa-project.org)"
)
Sa1normativeplot
ggsave("Study1a-norms.png", dpi = 600, scale = 1.7)


Sa1regretplot <- ggstatsplot::gghistostats(
  data = data1, # data from which variable is to be taken
  x = regret, # numeric variable
  xlab = "Regret", # x-axis label
  # title = "Preference", # title for the plot
  #ggtheme = ggthemes::theme_tufte(), # changing default theme
  test.value = 0, # test value
  #caption = "Data courtesy of: SAPA project (https://sapa-project.org)"

)
Sa1regretplot
ggsave("Study1a-regret.png", dpi = 600, scale = 1.7)

# two in one
library(ggpubr)
ggarrange(Sa1preferenceplot, Sa1competenceplot, Sa1normativeplot, Sa1regretplot, common.legend = TRUE)
ggsave("Study1a-4 in one.png", width = 11, height = 10, dpi = 600, scale = 1)



preference<-t.test(data1$preference, mu = 0)
reportpref1<-report(preference)
competence <- t.test(data1$competence, mu = 0)
report(competence)
normative<-t.test(data1$normative, mu = 0)
report(normative)
regret<-t.test(data1$regret, mu = 0)
report(regret)

```


# Study 1b

```{r study 1b, echo=FALSE}

data1b <- read.csv("inactionwetrust_study1b.csv")

# data cleaning
data1b <- data1b[-c(1:2),]

## remove variable descriptions + practice data
data1b <-  data1b [, c("preference", "competence", "normative","Q55",
                       "check_1", "check_2", "check_3", "gender", "age")]
# descriptives
data1b$preference <- as.numeric(data1b$preference)
data1b$competence <- as.numeric(data1b$competence)
data1b$normative <- as.numeric(data1b$normative)
data1b<-rename(data1b, regret = Q55)
data1b$regret <- as.numeric(data1b$regret)
data1b$age<-as.numeric(data1b$age)

summary1b <- data1b %>%
    select(preference, competence, normative, regret, gender, age) %>% 
  psych::describe(quant=c(.25,.75)) %>% as_tibble(rownames="rowname")
knitr::kable(summary1b, digits=2, caption = "Summary descriptives", align = "c")
tablegender<-table(data1b$gender)
knitr::kable(tablegender, digits=2, caption = "Summary gender", align = "c")


dplot1b <- data1b %>% select(preference, competence, normative, regret)%>%
  rename(Preference = preference, Competence = competence, Norms = normative, Regret = regret)%>%
  gather()
dplot1b$key<-factor(dplot1b$key, levels = c("Preference","Competence", "Norms", "Regret"))
dplot1b  %>% ggplot(aes(value)) +
  facet_wrap(~ key, scales = "free")+ geom_histogram(binwidth = 1)+theme_apa()+
  labs(x = "", y = "")+ scale_x_continuous(limits = c(-5,0, 5))+ ylim(0, 200)


S1bpreferenceplot <- ggstatsplot::gghistostats(
  data = data1b, # data from which variable is to be taken
  x = preference, # numeric variable
  xlab = "Preference", # x-axis label
  # title = "Preference", # title for the plot
  #ggtheme = ggthemes::theme_tufte(), # changing default theme
  test.value = 0, # test value
  #caption = "Data courtesy of: SAPA project (https://sapa-project.org)"
)
S1bpreferenceplot
ggsave("Study1b-preference.png", dpi = 600, scale = 1.7)

S1bcompetenceplot <- ggstatsplot::gghistostats(
  data = data1b, # data from which variable is to be taken
  x = competence, # numeric variable
  xlab = "Competence", # x-axis label
  # title = "Competence", # title for the plot
  #ggtheme = ggthemes::theme_tufte(), # changing default theme
  test.value = 0, # test value
  #caption = "Data courtesy of: SAPA project (https://sapa-project.org)"
)
S1bcompetenceplot
ggsave("Study1b-competence.png", dpi = 600, scale = 1.7)


S1bnormativeplot <- ggstatsplot::gghistostats(
  data = data1b, # data from which variable is to be taken
  x = normative, # numeric variable
  xlab = "Norms", # x-axis label
  # title = "Norms", # title for the plot
  #ggtheme = ggthemes::theme_tufte(), # changing default theme
  test.value = 0, # test value
  #caption = "Data courtesy of: SAPA project (https://sapa-project.org)"
)
S1bnormativeplot
ggsave("Study1b-norms.png", dpi = 600, scale = 1.7)


S1bregretplot <- ggstatsplot::gghistostats(
  data = data1b, # data from which variable is to be taken
  x = regret, # numeric variable
  xlab = "Regret", # x-axis label
  # title = "Preference", # title for the plot
  #ggtheme = ggthemes::theme_tufte(), # changing default theme
  test.value = 0, # test value
  #caption = "Data courtesy of: SAPA project (https://sapa-project.org)"
)
S1bregretplot
ggsave("Study1b-regret.png", dpi = 600, scale = 1.7)

# two in one
library(ggpubr)
ggarrange(S1bpreferenceplot, S1bcompetenceplot, S1bnormativeplot, S1bregretplot, common.legend = TRUE)
ggsave("Study1b-4 in one.png", width = 11, height = 10, dpi = 600, scale = 1)

preferenceb<-t.test(data1b$preference, mu = 0)
report(preferenceb)
competenceb <- t.test(data1b$competence, mu = 0)
report(competenceb)
normativeb<-t.test(data1b$normative, mu = 0)
report(normativeb)
regretb<-t.test(data1b$regret, mu = 0)
report(regretb)


```

# Study 2

```{r study 2, echo=FALSE}

data2 <- read.csv("inactionwetrust_study2.csv",sep = ";" )
# data cleaning
# data2 <- data2[-c(1:2),]
## remove variable descriptions + practice data
data2 <-  data2 [, c("expect", "preference", "competence", "descriptive.norms", "Injunctive", "regret", "joy", "check", "gender", "age", "condition")]
data2 <- mutate_all(data2, function(x) as.numeric(as.character(x)))

# Manipuation check
# check question about to what extent participants expect the advisors to change their behaviour (based on prior outcomes) : negative prior outcome > no prior outcome > positive prior outcome
# 1 = absent/control, 2 = positive 3 = negative

datasetexpect12 <-data2 %>% select (expect, condition) %>% filter (condition == 1 | condition == 2)
check1<-t.test(datasetexpect12$expect~datasetexpect12$condition)
check1

datasetexpect13 <-data2 %>% select (expect, condition) %>% filter (condition == 1 | condition == 3)
check3<-t.test(datasetexpect13$expect~datasetexpect13$condition)
check3

```

As expected, positive prior outcome was found with lower change to advisors behavior than absent prior outcome, m1=`r check1$estimate[2]`, m2= `r check1$estimate[1]`, t(`r check1$parameter`)=`r check1$statistic`, p = `r check1$p.value`.
Likewise, absent prior outcome was found with lower change to advisors behavior than negative prior outcome, m = `r check3$estimate[2]`, t(`r check3$parameter`)=`r check3$statistic`, p = `r check3$p.value`.
The check is successful.

```{r descriptives2}

S2Control <- data2 %>% filter (condition == 1)

summary2 <- S2Control %>%
    select(preference, competence, descriptive.norms, Injunctive, regret, joy, age, gender) %>% 
  psych::describe(quant=c(.25,.75)) %>% as_tibble(rownames="rowname")
knitr::kable(summary2, digits=2, caption = "Summary descriptives", align = "c")
tablegender2<-table(S2Control$gender)
knitr::kable(tablegender2, digits=2, caption = "Summary gender", align = "c")

dplot2 <- S2Control %>% 
  select(preference, competence, descriptive.norms, Injunctive, regret, joy) %>%
  rename(Preference = preference, Competence = competence,
         "Descriptive norms" = descriptive.norms,
         "Injunctive norms" = Injunctive, Regret = regret, Joy = joy)%>%
  gather()
dplot2$key<-factor(dplot2$key, levels = c("Preference","Competence",
                                          "Descriptive norms", "Injunctive norms",
                                          "Regret", "Joy"))

dplot2 %>% ggplot(aes(value)) + 
  facet_wrap(~ key, scales = "free")+ geom_histogram(binwidth = 1)+theme_apa()+
  labs(x = "", y = "")+ scale_x_continuous(limits = c(-5,0,5))+ ylim(0, 250) 


S2preferenceplot <- ggstatsplot::gghistostats(
  data = S2Control, # data from which variable is to be taken
  x = preference, # numeric variable
  xlab = "Preference", # x-axis label
  # title = "Preference", # title for the plot
  #ggtheme = ggthemes::theme_tufte(), # changing default theme
  test.value = 0, # test value
  #caption = "Data courtesy of: SAPA project (https://sapa-project.org)"
)
S2preferenceplot
ggsave("Study2-preference.png", dpi = 600, scale = 1.7)

S2competenceplot <- ggstatsplot::gghistostats(
  data = S2Control, # data from which variable is to be taken
  x = competence, # numeric variable
  xlab = "Competence", # x-axis label
  # title = "Competence", # title for the plot
  #ggtheme = ggthemes::theme_tufte(), # changing default theme
  test.value = 0, # test value
  #caption = "Data courtesy of: SAPA project (https://sapa-project.org)"
)
S2competenceplot
ggsave("Study2-competence.png", dpi = 600, scale = 1.7)


S2desnormativeplot <- ggstatsplot::gghistostats(
  data = S2Control, # data from which variable is to be taken
  x = descriptive.norms, # numeric variable
  xlab = "Descriptive norms", # x-axis label
  # title = "Norms", # title for the plot
  #ggtheme = ggthemes::theme_tufte(), # changing default theme
  test.value = 0, # test value
  #caption = "Data courtesy of: SAPA project (https://sapa-project.org)"
)
S2desnormativeplot
ggsave("Study2-descriptive-norms.png", dpi = 600, scale = 1.7)

S2injnormativeplot <- ggstatsplot::gghistostats(
  data = S2Control, # data from which variable is to be taken
  x = Injunctive, # numeric variable
  xlab = "Injunctive norms", # x-axis label
  # title = "Norms", # title for the plot
  #ggtheme = ggthemes::theme_tufte(), # changing default theme
  test.value = 0, # test value
  #caption = "Data courtesy of: SAPA project (https://sapa-project.org)"
)
S2injnormativeplot
ggsave("Study2-injunctive-norms.png", dpi = 600, scale = 1.7)

S2regretplot <- ggstatsplot::gghistostats(
  data = S2Control, # data from which variable is to be taken
  x = regret, # numeric variable
  xlab = "Regret", # x-axis label
  # title = "Preference", # title for the plot
  #ggtheme = ggthemes::theme_tufte(), # changing default theme
  test.value = 0, # test value
  #caption = "Data courtesy of: SAPA project (https://sapa-project.org)"
)
S2regretplot
ggsave("Study2-regret.png", dpi = 600, scale = 1.7)

S2joyplot <- ggstatsplot::gghistostats(
  data = S2Control, # data from which variable is to be taken
  x = joy, # numeric variable
  xlab = "Joy", # x-axis label
  # title = "Preference", # title for the plot
  #ggtheme = ggthemes::theme_tufte(), # changing default theme
  test.value = 0, # test value
  #caption = "Data courtesy of: SAPA project (https://sapa-project.org)"
)
S2joyplot
ggsave("Study2-joy.png", dpi = 600, scale = 1.7)


# six in one
library(ggpubr)
ggarrange(S2preferenceplot, S2competenceplot, S2desnormativeplot, S2injnormativeplot, S2regretplot, S2joyplot, ncol = 2, nrow	= 3, common.legend = TRUE)
ggsave("Study2-control-6 in one.png", width = 12, height = 18, dpi = 600, scale = 1)


preference2<-t.test(S2Control$preference, mu = 0)
report(preference2)
competence2 <- t.test(S2Control$competence, mu = 0)
report(competence2)
descriptive.norms2<-t.test(S2Control$descriptive.norms, mu = 0)
report(descriptive.norms2)
Injunctive2<-t.test(S2Control$Injunctive, mu = 0)
report(Injunctive2)
regret2<-t.test(S2Control$regret, mu = 0)
report(regret2)
joy2<-t.test(S2Control$joy, mu = 0)
report(joy2)


```

### differences between conditions

#1. In case of no prior outcomes or positive prior outcomes, the advisor that did not act will be preferred over the one who did act, assuming both action and inaction led to negative outcomes. Additionally, we predict that the advisor who did not act will be seen as more competent, and that his decision will be seen as more in line with social norms (injunctive and descriptive). 
less than 0 : Paul = inaction
more than 0 : George = action
we want the t-test being significantly lower than 0

Test for no prior outcomes or positive prior outcomes:

```{r diff between condition}

data2$conditionrecode <- recode(data2$condition, '1' = "Control", '2' = "Positive", '3' = "Negative", .default = NA_character_)

S2anovapreference <- ggstatsplot::ggbetweenstats(
  data = data2,
  x = conditionrecode,
  y = preference,
  xlab = "Condition",
  ylab = "Preference",
  point.path = FALSE,
  point.args = list(size = 4, alpha = 0.2, 
                    position = ggplot2::position_jitterdodge(jitter.width = 0.4, jitter.height = 0.4)),
  # centrality.point.args = list(size = 7, alpha = 0.7, color="#b30000"),
  # ggtheme = ggstatsplot::theme_ggstatsplot(),
  # violin.args = list(width = 1, alpha = 0.2),
  bf.message = TRUE,
  plot.type = "violin",
  results.subtitle = TRUE
  # effsize.type = "d"
)
S2anovapreference
ggsave("Study2-anova-preference.png", dpi = 600, scale = 1)

S2anovacompetence <- ggstatsplot::ggbetweenstats(
  data = data2,
  x = conditionrecode,
  y = competence,
  xlab = "Condition",
  ylab = "Competence",
  point.path = FALSE,
  point.args = list(size = 4, alpha = 0.2, 
                    position = ggplot2::position_jitterdodge(jitter.width = 0.4, jitter.height = 0.4)),
  # centrality.point.args = list(size = 7, alpha = 0.7, color="#b30000"),
  # ggtheme = ggstatsplot::theme_ggstatsplot(),
  # violin.args = list(width = 1, alpha = 0.2),
  bf.message = TRUE,
  plot.type = "violin",
  results.subtitle = TRUE
  # effsize.type = "d"
)
S2anovacompetence
ggsave("Study2-anova-competence.png", dpi = 600, scale = 1)

S2anovadescnorms <- ggstatsplot::ggbetweenstats(
  data = data2,
  x = conditionrecode,
  y = descriptive.norms,
  xlab = "Condition",
  ylab = "Descriptive norms",
  point.path = FALSE,
  point.args = list(size = 4, alpha = 0.2, 
                    position = ggplot2::position_jitterdodge(jitter.width = 0.4, jitter.height = 0.4)),
  # centrality.point.args = list(size = 7, alpha = 0.7, color="#b30000"),
  # ggtheme = ggstatsplot::theme_ggstatsplot(),
  # violin.args = list(width = 1, alpha = 0.2),
  bf.message = TRUE,
  plot.type = "violin",
  results.subtitle = TRUE
  # effsize.type = "d"
)
S2anovadescnorms
ggsave("Study2-anova-descnorms.png", dpi = 600, scale = 1)


S2anovainjnorms <- ggstatsplot::ggbetweenstats(
  data = data2,
  x = conditionrecode,
  y = Injunctive,
  xlab = "Condition",
  ylab = "Injunctive norms",
  point.path = FALSE,
  point.args = list(size = 4, alpha = 0.2, 
                    position = ggplot2::position_jitterdodge(jitter.width = 0.4, jitter.height = 0.4)),
  # centrality.point.args = list(size = 7, alpha = 0.7, color="#b30000"),
  # ggtheme = ggstatsplot::theme_ggstatsplot(),
  # violin.args = list(width = 1, alpha = 0.2),
  bf.message = TRUE,
  plot.type = "violin",
  results.subtitle = TRUE
  # effsize.type = "d"
)
S2anovainjnorms
ggsave("Study2-anova-injnorms.png", dpi = 600, scale = 1)

S2anovaregret <- ggstatsplot::ggbetweenstats(
  data = data2,
  x = conditionrecode,
  y = regret,
  xlab = "Condition",
  ylab = "Regret",
  point.path = FALSE,
  point.args = list(size = 4, alpha = 0.2, 
                    position = ggplot2::position_jitterdodge(jitter.width = 0.4, jitter.height = 0.4)),
  # centrality.point.args = list(size = 7, alpha = 0.7, color="#b30000"),
  # ggtheme = ggstatsplot::theme_ggstatsplot(),
  # violin.args = list(width = 1, alpha = 0.2),
  bf.message = TRUE,
  plot.type = "violin",
  results.subtitle = TRUE
  # effsize.type = "d"
)
S2anovaregret
ggsave("Study2-anova-regret.png", dpi = 600, scale = 1)

S2anovajoy <- ggstatsplot::ggbetweenstats(
  data = data2,
  x = conditionrecode,
  y = joy,
  xlab = "Condition",
  ylab = "Joy",
  point.path = FALSE,
  point.args = list(size = 4, alpha = 0.2, 
                    position = ggplot2::position_jitterdodge(jitter.width = 0.4, jitter.height = 0.4)),
  # centrality.point.args = list(size = 7, alpha = 0.7, color="#b30000"),
  # ggtheme = ggstatsplot::theme_ggstatsplot(),
  # violin.args = list(width = 1, alpha = 0.2),
  bf.message = TRUE,
  plot.type = "violin",
  results.subtitle = TRUE
  # effsize.type = "d"
)
S2anovajoy
ggsave("Study2-anova-joy.png", dpi = 600, scale = 1)

# six in one
library(ggpubr)
ggarrange(S2anovapreference, S2anovacompetence, S2anovadescnorms, S2anovainjnorms, S2anovaregret, S2anovajoy)
ggsave("Study2-anova-6 in one.png", width = 15, height = 10, dpi = 600, scale = 1)


datasetexpect12 <-data2 %>% select (condition, preference, competence, Injunctive, descriptive.norms) %>% filter (condition <3)



preference12<-t.test(datasetexpect12$preference, mu = 0)
report(preference12)
competence12<-t.test(datasetexpect12$competence, mu = 0)
report(competence12)
Injunctive12<-t.test(datasetexpect12$Injunctive, mu = 0)
report(Injunctive12)
descriptive.norms12<-t.test(datasetexpect12$descriptive.norms, mu = 0)
report(descriptive.norms12)

```

2. In case of negative prior outcomes, the advisor who did act will be preferred over the one who did not act, assuming both action and inaction led to negative outcomes. Finally, we predict that the advisor who did act will be seen as more competent, and that his decision will be seen as more in line with social norms (injunctive and descriptive). 

we want the t-test being significantly higher than 0

Test for Negative prior outcomes:

```{r negative condition}

datasetexpect3 <-data2 %>% select (condition, preference, competence, Injunctive, descriptive.norms) %>% filter (condition ==3)

preference3<-t.test(datasetexpect3$preference, mu = 0)
report(preference3)
competence3<-t.test(datasetexpect3$competence, mu = 0)
report(competence3)
Injunctive3<-t.test(datasetexpect3$Injunctive, mu = 0)
report(Injunctive3)
descriptive.norms3<-t.test(datasetexpect3$descriptive.norms, mu = 0)
report(descriptive.norms3)
 


```

We will also look at the correlations between regret, joy, competence, normativeness, and hiring preferences and expect them to be related positively with each other generally.

For study 1
```{r correlation1}

corrdf1<-data1%>%select (competence, preference, normative, regret)%>%na.omit(corrdf1)
correlate1<-cor(corrdf1, method = "pearson")
p<-rcorr(as.matrix(corrdf1), type="pearson")
corrplot(correlate1)
chart.Correlation(corrdf1, histogram=TRUE, pch=19)
corr_ci(data1)

```



For study 1b
```{r correlation1b}

corrdf1b<-data1b%>%select (competence, preference, normative, regret)%>%na.omit(corrdf1b)
correlate1b<-cor(corrdf1b, method = "pearson")
rcorr(as.matrix(corrdf1b), type="pearson")
corrplot(correlate1b)
chart.Correlation(corrdf1b, histogram=TRUE, pch=19)
cor.test(data1$competence, data1$preference)
corr_ci(data1b)

```



For study 2
```{r correlation2}

nopriorcorrdf<-data2%>%select (regret, joy, competence, Injunctive, descriptive.norms, preference, condition)%>%filter (condition == 1) %>% na.omit(nopriorcorrdf)%>%select(-condition)
positivepriorcorrdf<-data2%>%select (regret, joy, competence, Injunctive, descriptive.norms, preference, condition)%>%filter (condition == 2) %>% na.omit(corrdf)%>%select(-condition)
negativepriorcorrdf<-data2%>%select (regret, joy, competence, Injunctive, descriptive.norms, preference, condition)%>%filter (condition == 3) %>% na.omit(negativepriorcorrdf)%>%select(-condition)

# these correlations are made using correlation package, who provide more details on the correlations
#nopriorcorrelate<-correlation::correlation(nopriorcorrdf, method = "pearson")
#positivepriorcorrelate<-correlation::correlation(positivepriorcorrdf, method = "pearson")
#negativepriorcorrelate<-correlation::correlation(negativepriorcorrdf, method = "pearson")


apa.cor.table(nopriorcorrdf, filename="nopriorcorrelation.doc",show.conf.interval = TRUE, show.sig.stars = FALSE, landscape = TRUE)
apa.cor.table(positivepriorcorrdf, filename="positivepriorcorrelation.doc",show.conf.interval = TRUE, show.sig.stars = FALSE, landscape = TRUE)
apa.cor.table(negativepriorcorrdf, filename="negativepriorcorrelation.doc",show.conf.interval = TRUE, show.sig.stars = FALSE, landscape = TRUE)


```
